The yaq Project: \\ Standardized Software Enabling Flexible Instrumentation

### 2023-03-16 SI.tex
SI cite bluesky
more SI typos

\subsection{\texttt{is\_busy} for ensuring order of operations}

@@

The Wright Group uses a purpose-built graphical program to perform data acquisition.
All of the hardware used is controlled via \yaq{}.
Data is collected using Bluesky, which runs in a background process.

@@

The Avro Specification \cite{AvroSpecification} specifically provides for compression codecs in the case of storing to disk, but there is nothing preventing the RPC pipe from similarly encoding the data, provided both ends of the communication support it.
EPICS provides a similar NDArray data type, which has individual image level compression configureable \cite{normative_types}.
Compression would allow larger arrays to be transported using fewer bytes over TCP, which would likely improve performance for large arrays where TCP transport is the bottleneck.
While TCP is the only currently supported transport layer for \yaq{}, this limitation could be lifted in the future.

>>>>

\subsection{\texttt{busy} for ensuring order of operations}

@@

The Wright Group uses a purpose-built graphical program to perform data acquisition.
All of the hardware used is controlled via \yaq{}.
Data is collected using Bluesky \cite{AllanDanielB2019a}, which runs in a background process.

@@

The Avro Specification \cite{AvroSpecification} specifically provides for compression codecs in the case of storing to disk, but there is nothing preventing the RPC pipe from similarly encoding the data, provided both ends of the communication support it.
EPICS provides a similar NDArray data type, which has individual image level compression configurable \cite{normative_types}.
Compression would allow larger arrays to be transported using fewer bytes over TCP, which would likely improve performance for large arrays where TCP transport is the bottleneck.
While TCP is the only currently supported transport layer for \yaq{}, this limitation could be lifted in the future.
